Adaptive Distance Metric Selection for Supervised Classification

### 2016-10-21 latex/Adaptive_distance_metric_notes.tex
test

\usepackage{fullpage,graphicx,amssymb,amsmath}
\usepackage{enumerate}
\usepackage{subfigure}
\usepackage{url}

@@

\section{Gershgorin Circle Theorem}

Reference \url{https://en.wikipedia.org/wiki/Gershgorin_circle_theorem}

Why do we care about this theorem? It provides a sufficient condition to ensure that a square matrix is positive semi-definite.

Let $\v{A}$ be a symmetric $n \times n$ matrix (hence, all eigenvalues are real).
Let $R_{i}=\sum _{j\neq {i}} \left|a_{ij}\right|$ be the sum of the absolute values of the non-diagonal entries in the $i$-th row. Let $D(a_{ii},R_{i})$ be the closed circle (or disc) centered at $a_{ii}$ with radius $R_{i}$. Such a disc is called a Gershgorin disc.

\begin{theorem}[Gershgorin Circle Theorem]
Every eigenvalue of $\v{A}$ lies within at least one of the Gershgorin discs $D(a_{ii},R_{i})$.
\end{theorem}

Let $\lambda^{\min}(\v{A})$ be the smallest eigenvalue of $\v{A}$ and let $\lambda_G^{\min}(\v{A}) = \min_{i=1,\ldots,n} \{a_{ii} - R_i\}$.
\begin{corollary}
If $\lambda_G^{\min}(\v{A}) \geq 0$, then $\v{A}$ is positive semi-definite. 
\end{corollary}
\proof Gershgorin's circle theorem asserts that $\lambda_G^{\min}(\v{A})$ is a lower bound on the minimum eigenvalue of $\v{A}$, i.e., $\lambda^{\min}(\v{A}) \geq \lambda_G^{\min}(\v{A})$.  One definition of a psd matrix is that all of its eigenvalues are non-negative. \qed

In our problem, we may require the matrix $\v{B}$ to be positive semi-definite.  Gershgorin's theorem tells us that this can be partially accomplished using linear programming techniques.  (I say ``partially'' because Gershgorin's theorem is not a necessary condition, thus it enforcing $\lambda_G^{\min}(\v{A}) \geq 0$ is actually a restriction, i.e., it may forbid some eligible psd matrices.  Nevertheless, it's an interesting starting point.)  To accomplish this with our matrix $\v{B}$, let $R_{k}(\v{B})=\sum _{\ell \neq k} \left|b_{k\ell}\right|$ and note that the condition $\lambda_G^{\min}(\v{B}) \geq 0$ implies that $\min_{k=1,\ldots,p} \{b_{kk} - R_k(\v{B})\} \geq 0$, which is equivalent to $b_{kk} - \sum _{\ell \neq k} \left|b_{k\ell}\right| \geq 0$ for all $k=1,\ldots,p$.  After introducing auxiliary non-negative decision variables $b^+_{k\ell}$ to model $|b_{k\ell}|$ for all $k \neq \ell$, the latter can be converted into a set of linear constraint as follows:
\begin{subequations} \label{model:gershgorin_restriction}
\begin{alignat}{4}
& b_{kk} - \sum _{\ell \neq k} b^+_{k\ell} \geq 0 && \qquad \forall k=1,\ldots,p \\
& b^+_{k\ell} \geq b_{k\ell} && \qquad \forall k=1,\ldots,p, \ell=1,\ldots,p~(k \neq \ell) \\
& b^+_{k\ell} \geq -b_{k\ell} && \qquad \forall k=1,\ldots,p, \ell=1,\ldots,p~(k \neq \ell) \\
& b^+_{k\ell} \geq 0 && \qquad \forall k=1,\ldots,p, \ell=1,\ldots,p~(k \neq \ell)
\end{alignat}
\end{subequations}

\todo[inline]{In the AIMMS code, we do not store the full $\v{B}$ matrix, but instead work only with the upper diagonal. Thus, it does not make sense to sum over all elements in row $k$ as written in $\sum _{\ell \neq k} b^+_{k\ell}$. Task: Write a similar version of constraints~\ref{model:gershgorin_restriction} in Latex. Implement these additional variables and constraints in AIMMS.  Also, include a binary parameter, say, PI-Require-PSD (use underscores) such that these new variables and constraints are only active if PI-Require-PSD = 1, i.e., you should put a conditional statement ``$|$ ~ PI-Require-PSD'' in the ``index domain'' of these new variables and constraints.
}

@@

\item Model \eqref{model:milp_with_outlier_detection}
works

show some pictures here

\item I did this and that
\end{itemize}
{\bf problems and questions:}
\begin{itemize}
\item queston 1
\item question 2

\end{itemize}
{\bf suggestions:}
\begin{itemize}
\item section \ref{sec:mimax_oneLamnda}
\end{itemize}

@@

\begin{itemize}
\item put here the ideas from excel
\end{itemize}

>>>>

\usepackage{fullpage,graphicx,amssymb,amsmath}
\usepackage{enumerate}
\usepackage{subfigure}

@@

@@

\item Model \eqref{model:milp_with_outlier_detection}
works. I did it in the aimms code "MILP SECTION4" Part.

\end{itemize}
{\bf problems and questions:}
\begin{itemize}
\item queston 1 How to show the certain points in the plots?
\item question 2

\end{itemize}

@@

\begin{itemize}
\item 1. Create new dataset -> e.g. 2 - Guassian with diffrent mu and Sigma
\item 2. ammend the code to add new point in a.g. Scatter Point
\item 3. Implement Optimization of Distance Metrix                 ACCOMPLISHED
\item 4. Add the robust version for section 4. (have just one lambda) both Latex and AIMS (PROCESSING)
\item 5. Create a performance profiles -- example 100 datasets and comapre 3-4 distance measures 
\item 6. add new codes for replacing "a delta"  -> to  "a |delta| "           ACCOMPLISHED
\item 7. add button to load instance          ACCOMPLISHED
\item 8. For Infesible problem we solved during the meeting why it was not infeasible                  ACCOMPLISHED

\end{itemize}
